---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edsdata

<!-- badges: start -->
<!-- badges: end -->

The `edsdata` package contains datasets for the textbook [Exploring Data Science with R and the Tidyverse: A Concise Introduction](https://ds4world.cs.miami.edu/) by Jerry Bonnell and Mitsunori Ogihara. 

## Installation

You can install the development version of edsdata from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jerrybonnell/edsdata")
```

## License 

Most of the datasets in this package are in the Public Domain and have a Creative Commons license. However, re-distributing the data through this package is not meant to cancel or to modify the existing licenses in any way. Please refer to the references in the `man` pages for information on any individual dataset.

## Package Contents 

```{r builddata, include=FALSE}
# code for parsing adapted from fosdata package description
# https://github.com/speegled/fosdata
library(edsdata)
library(tidyverse)
sets <- vcdExtra::datasets("edsdata")
get_source <- Vectorize(function(dset) {
  
    thefile <- help(dset, package="edsdata")
    Rd <- utils:::.getHelpFile(thefile)
    names(Rd) <- substring(sapply(Rd, attr, "Rd_tag"),2)
    temp_args <- Rd$arguments
    
    Rd$arguments <- NULL
    myrd <- lapply(Rd, unlist)
    myrd <- lapply(myrd, paste, collapse="")
    
    temp_args <- temp_args[sapply(temp_args , attr, "Rd_tag") == "\\item"]
    temp_args <- lapply(temp_args, lapply, paste, collapse="")
    temp_args <- lapply(temp_args, "names<-", c("arg", "description"))
    myrd$arguments <- temp_args
    
    myrd$source
})

sets <- sets |>
  mutate(Source = get_source(Item))
```

```{r showdata, echo=FALSE}
sets %>% select(Item, Title, dim) %>%
  knitr::kable(col.names = c("Name","Description","Dim (RxC)"))
```

## Citation

To cite the package `edsdata` in publications, use:

```{r echo=FALSE, results='asis'}
print(citation("edsdata"), style="text")
```

A BibTeX entry for LaTeX users is:

```{r echo=FALSE, comment=NA}
print(citation("edsdata"), style="bibtex")
```

## References

```{r showrefs, echo=FALSE, results='asis'}
for (i in 1:nrow(sets)) {
  if (!is.na(sets$Source[i])) {
    cat('####',sets$Item[i],'\n',unlist(sets$Source[i]),'\n')
  }
}
```

